### 2014-11-13 tex/results.tex

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of \symtxt{} at
analyzing programs with unbounded complex data input in the context of
symbolic execution. In order to perform our evaluation we implement
the \symtxt{} technique and evaluate its efficiacy on three Java data
structure artifacts. We compare the results of \symtxt{} with other
state of the art techniques that initialize complex data input
symbolically. We first describe the tool infrastructure we use to
implement our approach.

\subsection{Tool Support}
We implement the \symtxt{} as an extension to the symbolic execution
engine of Java PathFinder(JPF)---Symbolic Pathfinder
(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10}. SPF is an
open source engine for performing symbolic execution on Java
bytecode. The JPF framework provides mechanism for overwriting the
execution semantics of the traditional concrete Java bytecode
semantics. SPF leverages this to define symbolic execution semantics
for Java bytecode. SPF performs a stateless search to generate the
symbolic execution tree since state matching in general is
undecidable.

SPF contains the implementation for GSE with lazy initialization. At
bytecodes that access uninitialized symbolic fields it creates custom
non-deterministic choices for the field to be null, new instance of
its type, and aliases to any previously initialized symbolic
fields~\cite{DBLP:journals/ase/PasareanuVBGMR13}. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

We create a new extension to SPF in order to implement the~\symtxt{}
approach. Even though our approach is presented using the Javalite
semantics, the implementation contains support for the full Java
semantics such as operations over integers and other data types
supported in Java. We overwrite three main sets of Java bytecodes that
map to the rewrite rules presented in~\secref{sec:precise}. We provide
custom implementation of the following: (i) field access bytecodes,
e.g., GETFIELD and ALOAD bytecodes, to implement the field-access and
summarize rules in~\figref{fig:symInit} and~\figref{fig:fHeap}(a),
(ii) the field write bytecodes, e.g., PUTFIELD and ASTORE bytecodes,
to implement the field-write rules in~\figref{fig:fHeap}(a), and (iii)
checking equality of references bytecode, IF\_ACMPEQ and IF\_ACMPNE,
to implement the equals references-true and references-false rules
in~\figref{fig:eqs}. \nsr{any custom implementation for integers? }

The default constraints library in SPF handles constraints in the CNF
form, these are unable to support constraints generated by \symtxt{}
approach since they contain disjunctions. Transforming the constraints
generated by \symtxt{} into a CNF form proved to be inefficient. We
use the \texttt{jConstraints} library that provides support to handle
arbitrary constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses
the z3 solver,~\cite{z3}, as the backend to solve the constraints. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

Loops and recursive methods over symbolic variables are bounded based
on some user-provided limit. These bounds are based on some
control-flow structure of the program and are often insufficient for
analyzing programs with input of complex data types as demonstrated
in~\cite{Kiasan07,Deng:2006}. In this work we use the $k$-bounding
technique that bounds the length of a reference chain from the root of
the heap~\cite{Deng:2006}.\nsr{check this!} Note we use $k$-bounding
because it preserves the functional equivalence of \gsetxt{}, lazier,
lazier\# and \symtxt{} techniques, a fact which can be established by
induction over the length of reference chains from a given initial
state. The $n$-bounding approach restricts the total number of
references created along a certain path. There is no easy way to
compare the number of references generated by \symtxt{} and other
techniques since \symtxt{} can create many references at a single
access point in its heap summary.

@@

To evaluate we use three Java data structure artifacts (a) Linked List
(b) Binary Search Tree, and (c) Tree Map. These data structures
programs are often used to the evaluate symbolic execution algorithms
with arbitrary heap inputs. The \emph{independent} variable in our
study is the algorithm for initializing symbolic references and the
$k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k-bound$ for each the algorithms. We select three dependent variables
and measures for our study: (i) time, (ii) states explored, and (iii)
paths generated. The \emph{time} is the total time taken by each
algorithm to explore the symbolic execution tree as well as total
constraint solving time. The \emph{states explored} represents the
number of nodes in the symbolic execution tree while the \emph{paths
  generated} represent as the name suggests the number of unique paths
in the symbolic execution tree.

>>>>

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
approach at analyzing programs with unbounded complex data input in
the context of symbolic execution. In order to perform our evaluation
we implement the \symtxt{} technique and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state of the art techniques that
initialize complex data input symbolically. We first describe the tool
infrastructure we use to implement our approach.

\subsection{Tool Support}
We implement the \symtxt{} as an extension to the symbolic execution
engine of Java PathFinder(JPF)---Symbolic Pathfinder
(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
is an open source engine for performing symbolic execution on Java
bytecode. SPF overwrites the concrete execution semantics of Java
bytecode to generate a symbolic execution tree. SPF contains an
implementation for GSE with lazy initialization. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

%since state matching in general is undecidable.  SPF leverages this
%to define symbolic execution semantics for Java bytecode.  At
%bytecodes that access uninitialized symbolic fields it creates custom
%non-deterministic choices for the field to be null, new instance of
%its type, and aliases to any previously initialized symbolic
%fields~\cite{} SPF performs a stateless search to generate the
%symbolic execution tree.

We create a new extension to SPF in order to implement the~\symtxt{}
approach. In addition to the operations presented in the Javalite
semantics, the implementation contains support for operations over
integers. Examples of bytecode that we overwrite in the SPF engine are
as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
bytecodes, to implement the field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}
(iv) linear arithmetic operations on integers and (v) comparison
operations on integers. We are currently working on adding support for
floating point operations, arrays, and bit-operations.

The default constraints library in SPF requires constraints to be in
the CNF form, and is unable to support constraints generated by the
\symtxt{} approach since they contain disjunctions. Transforming the
constraints generated by the \symtxt{} approach into a CNF form proved
to be inefficient. We use the \texttt{jConstraints} library that
provides support to handle arbitrary
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver,~\cite{z3}, as the backend to solve the constraints. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

\begin{comment}
Loops and recursive methods over symbolic variables are bounded based
on some user-provided limit. These bounds are based on some
control-flow structure of the program and are often insufficient for
analyzing programs with input of complex data types as demonstrated
in~\cite{Kiasan07,Deng:2006}. In this work we use the $k$-bounding
technique that bounds the length of a reference chain from the root of
the heap~\cite{Deng:2006}.\nsr{check this!} Note we use $k$-bounding
because it preserves the functional equivalence of \gsetxt{}, lazier,
lazier\# and \symtxt{} techniques, a fact which can be established by
induction over the length of reference chains from a given initial
state. The $n$-bounding approach restricts the total number of
references created along a certain path. There is no easy way to
compare the number of references generated by \symtxt{} and other
techniques since \symtxt{} can create many references at a single
access point in its heap summary.
\end{comment}

@@

To evaluate we use three Java data structure artifacts (a) Linked List
(b) Binary Search Tree, and (c) Tree Map. These data structures
programs are often used to the evaluate symbolic execution algorithms
with arbitrary heap inputs. The \emph{independent} variable in our
study is the algorithm for initializing symbolic references and the
$k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k$-bound for each the algorithms. Note that $k$-bounding bounds the
length of a reference chain from the root of the heap~\cite{Deng:2006}
We select three dependent variables and measures for our study: (i)
time, (ii) states explored, and (iii) paths generated. The \emph{time}
is the total time taken by each algorithm to explore the symbolic
execution tree as well as total constraint solving time. The
\emph{states explored} represents the number of nodes in the symbolic
execution tree while the \emph{paths generated} represent as the name
suggests the number of unique paths in the symbolic execution tree.
